%
%--- 
%-----------------------------------
\chapter{Conclusion}
\label{ch:conclusion}
%-----------------------------------
%--- 
%

In this Master's degree work, we proposed and implemented a Monte Carlo simulation to estimate experimental quantities of narrow-line magneto-optical traps. We essentially estimate the probability distributions of the atoms' position and velocity in the presence of laser light and a quadrupole magnetic field. Then, with these distributions, we estimate the atomic cloud profile and the temperature. Our proposal is to sample the atoms' states by considering their movement as a Markovian process.

We were able to simulate three nMOT arrangements reproduced by different laboratories and obtain estimated quantities that are more accurate than the theoretical ones. It is possible to use our simulation to optimize parameters of nMOTs without the necessity of experimental data. It is also a tool to analyse the feasibility of unusual nMOT arrangements such as nMOTs with fewer laser beams.

We analysed the limits of our model regarding the three nMOT regimes and verified that it works exclusively in the power-broadened regime. Therefore, to obtain accurate quantities, it is necessary to guarantee a set of parameters that keep the nMOT in this regime. We validated our model for nMOTs with small and slightly large narrownesses. It is possible to estimate quantities for both cases, but the larger the narrowness, the more difficult it is to reach the power-broadened regime. Hence, nMOTs with small narrownesses have a larger range in which we are able to predict experimental quantities. The nMOT setup with a slightly large narrowness must be designed to decrease the trapping effect in the gravity direction so that the atoms are able to fall under gravity. This is a typical effect of power-broadened nMOTs.

We confirmed that our simulation is capable of estimating quantities for complicated transitions by assuming the spin-polarized atoms. In our model, we are assuming that the transition is a four-level system. The dysprosium nMOT presented in Section \ref{sec:dysprosium} is based on an electronic transition with 36 states. Nevertheless, we were able to estimate quantities by assuming spin-polarized atoms based on previous works in which this phenomenon was observed experimentally.


%The magneto-optical traps are the workhorse of laser cooling. They were essential for at least two Nobel Prize laureates works since they allowed a myriad of remarkable achievements such as the Bose-Einstein condensation, accurate atomic clocks, quantum computers, and quantum sensors. Although MOTs work well experimentally, the theory of MOTs does not provide accurate predictions for some experimental quantities. The case of narrow-line MOTs is even more complicated due to the gravity effect.

%The first part of this work was focused on to understand the interaction between atoms and light, which is essential to study MOTs properly. from two approaches. The first one is the rate equations model proposed by Albert Einstein. We explored such approach to get start to basic concepts. The second approach is the optical Bloch equations, which contemplates coherent effects and fundamental understanding of the line broadening mechanisms. We then deduced and analysed the optical forces, which is a key concept to understand the theory of the magneto-optical trap. We introduced the MOT theory by an simply one-dimension model. Afterwards, we presented the three-dimensional case as well as the narrow-line magneto-optical trap.

